Data_visualization

### 2018-06-20 Rmd/Data_visualization.Rmd
adding family to ovules plot
working on data visualization for meeting

# Ovules per family, **Convolvulaceae is constant 4 or 6**

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=4}
#load libraries

@@

par(mfrow=c(2,1))

d<-read.csv("Data/Ovules.csv", sep=";")
d<- d[,-c(9,11)]
colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"
colnames(d)[9]<-"I. aquatica"
colnames(d)[10]<-"I. purpurea"

@@

@@

>>>>

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
#load libraries

@@

par(mfrow=c(2,1))
d<-read.csv("Data/Ovules.csv", sep=";")
d<- d[,-c(9,11)]
colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"
colnames(d)[9]<-"I. aquatica"
colnames(d)[10]<-"I. purpurea"

@@

family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))

d[,"family"] <- family

@@

```{r echo=FALSE, out.width='80%', fig.align='center'}
knitr::include_graphics('Images/all_species.png')
```
